Windowed Developer Topic Analysis

### 2009-04-06 lda-paper.tex
more lda paper

We propose to extend the use of common topic analysis techniques by
executing them over windows of documents over time. We hope by looking
at topic clusters over time we can identify continuous effort on a
select group of topics. Figure \ref{fig:lda} is an example of the kind
of visualization we want to automatically generate. We want to see
topics which are unique to a certain time period, displayed across the
time axis. Those topics that reoccur, or occur over a larger period
are plotted continuously. In our example we have summarized the topics
with a single word.

@@

>>>>

We propose to extend the use of common topic analysis techniques by
executing them over windows of documents over time. We hope by looking
at topic clusters during periods or windows over time we can identify
continuous effort on a select group of topics as well reflect topics
that were local to that period. Figure \ref{fig:lda} is an example of
the kind of visualization we want to automatically generate. We want
to see topics which are unique to a certain time period, displayed
across the time axis. Those topics that reoccur, or occur over a
larger period are plotted continuously. In our example we have
summarized the topics with a single word.

@@

Our methodology is to first extract the commits from repositories such
as CVS or Bitkeeper. Then we extract the revisions and commits,
grouping the revisions into commits if necessary. We extract the
commit log message of each commit, count the occurence of each word in
the message, remove stop words, and then produce word distributions
for each message.
